A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2019-08-23 README.Rmd
reorder readme

This is the accompanying GitHub repository to a work in progress paper, its abstract reads:

>>>>

The repo is maintained by [Aaron Peikert ![ORCID iD](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0001-7813-818X) and [Andreas Brandmaier ![ORCID iD](https://orcid.org/sites/default/files/images/orcid_16x16.png)](http://orcid.org/0000-0001-8765-6982) [![licensebuttons by](https://licensebuttons.net/l/by/3.0/88x31.png)](https://creativecommons.org/licenses/by/4.0)

This is the accompanying GitHub repository to a work in progress paperby Aaron Peikert[![ORCID iD](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0001-7813-818X) and Andreas Brandmaier [![ORCID iD](https://orcid.org/sites/default/files/images/orcid_16x16.png)](http://orcid.org/0000-0001-8765-6982).

# Abstract
